Lifespan analysis

### 2023-06-07 paper/manuscript.Rmd
play around with model plots; add lifespan sample descr to manuscript

```{r dev_sample}
lifespan_sample <- tango_lifespan %>% 
  group_by(age_group) %>%
  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
  summarise(
    n_total = n_distinct(subj_id), 
    age_mean = mean(age, na.rm = T) %>% round(2),
    age_sd = sd(age, na.rm = T) %>% round(2),
    age_min = min(age, na.rm = T),
    age_max = max(age, na.rm = T),
    n_females = ceiling(sum(female/15)),
  )
```

@@

The remote child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` children, including `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "3"])` 3-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "3"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "3"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "3"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "3"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "3"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "4"])` 4-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "4"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "4"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "4"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "4"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "4"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "5"])` 5-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "5"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "5"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "5"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "5"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "5"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "6"])` 6-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "6"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "6"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "6"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "6"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "6"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "7"])` 7-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "7"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "7"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "7"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "7"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "7"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "8"])` 8-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "8"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "8"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "8"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "8"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "8"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "9"])` 9-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "9"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "9"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "9"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "9"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "9"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "10"])` 10-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "10"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "10"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "10"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "10"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "10"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "11"])` 11-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "11"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "11"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "11"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "11"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "11"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "12"])` 12-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "12"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "12"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "12"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "12"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "12"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "13"])` 13-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "13"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "13"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "13"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "13"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "13"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "14"])` 14-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "14"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "14"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "14"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "14"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "14"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "15"])` 15-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "15"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "15"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "15"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "15"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "15"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "16"])` 16-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "16"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "16"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "16"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "16"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "16"])` girls), and `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "17"])` 17-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "17"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "17"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "17"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "17"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "17"])` girls).

@@

<!-- Adults were recruited via *Prolific* [@palan2018prolific]. *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool. Participants consisted of `r lifespan_sample$n_total` English-speakers with an average age of `r lifespan_sample$age_mean` years (SD = `r lifespan_sample$age_sd`, range = `r lifespan_sample$age_min` - `r lifespan_sample$age_max`, `r lifespan_sample$n_females` females). -->

@@

```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
knitr::include_graphics("../figures/magnet_procedure.png")
```

@@

```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
knitr::include_graphics(c("../figures/tango_dev.png"))
```

>>>>

```{r lifespan_sample}
lifespan_sample <- readRDS("../saves/lifespan_sample.rds")
```

@@

The remote child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` children, including `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "3"])` 3-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "3"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "3"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "3"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "3"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "3"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "4"])` 4-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "4"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "4"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "4"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "4"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "4"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "5"])` 5-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "5"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "5"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "5"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "5"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "5"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "6"])` 6-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "6"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "6"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "6"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "6"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "6"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "7"])` 7-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "7"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "7"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "7"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "7"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "7"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "8"])` 8-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "8"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "8"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "8"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "8"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "8"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "9"])` 9-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "9"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "9"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "9"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "9"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "9"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "10"])` 10-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "10"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "10"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "10"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "10"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "10"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "11"])` 11-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "11"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "11"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "11"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "11"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "11"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "12"])` 12-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "12"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "12"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "12"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "12"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "12"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "13"])` 13-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "13"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "13"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "13"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "13"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "13"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "14"])` 14-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "14"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "14"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "14"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "14"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "14"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "15"])` 15-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "15"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "15"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "15"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "15"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "15"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "16"])` 16-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "16"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "16"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "16"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "16"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "16"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "17"])` 17-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "17"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "17"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "17"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "17"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "17"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "18"])` 17-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "18"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "18"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "18"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "18"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "18"])` girls), 
`r sum(lifespan_sample$n_total[lifespan_sample$age_group == "19"])` 17-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "19"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "19"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "19"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "19"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "19"])` girls).

@@

Adults were recruited via *Prolific* [@palan2018prolific]. *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool. Participants consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group >= 20])` English-speaking adults that reported to have normal or corrected-to-normal vision. The sample included `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "20"])` 20- to 29-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "20"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "20"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "20"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "20"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "20"])` female), 
`r sum(lifespan_sample$n_total[lifespan_sample$age_group == "30"])` 30- to 39-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "30"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "30"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "30"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "30"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "30"])` female),
`r sum(lifespan_sample$n_total[lifespan_sample$age_group == "40"])` 40- to 49-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "40"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "40"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "40"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "40"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "40"])` female),
`r sum(lifespan_sample$n_total[lifespan_sample$age_group == "50"])` 50- to 59-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "50"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "50"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "50"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "50"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "50"])` female),
`r sum(lifespan_sample$n_total[lifespan_sample$age_group == "60"])` 60- to 69-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "60"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "60"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "60"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "60"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "60"])` female), and
`r sum(lifespan_sample$n_total[lifespan_sample$age_group == "70"])` 70- to 79-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "70"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "70"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "70"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "70"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "70"])` female).

@@

```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
knitr::include_graphics("../figures/procedure.png")
```

@@

```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
knitr::include_graphics(c("../figures/lifespan_plot.png"))
```

### 2023-06-07 stats/lifespan.Rmd
play around with model plots; add lifespan sample descr to manuscript

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidybayes) # for stat_halfeye, add_predictive_draws
library(brms) # modeling
library(cmdstanr) # modeling
check_cmdstan_toolchain(fix = TRUE, quiet = TRUE)

@@

# ggsave("../figures/lifespan.png", width = 8, height = 4, scale = 1.2)
saveRDS(lifespan_plot, "../saves/lifespan_plot.rds")
```

@@

```{r prediction_plot_winning_model}
 mdraws <- mdata %>%
  add_predicted_draws(msplines) %>% 
  ungroup() %>% 
  select(-c(.row, .chain, .iteration)) %>%
  rename(draw = .draw, predicted_value = .prediction)

write.csv(mdraws, "../saves/lifespan_mdraws.csv", quote = F, row.names = F)
saveRDS(mdraws, "../saves/lifespan_mdraws.rds")

prediction_plot <- mdraws %>%
  ggplot(aes(x = age)) +  
  geom_jitter(aes(y = mean_dist), colour = "grey", size = 1.5, alpha = 0.8) + 
  stat_lineribbon(aes(y = predicted_value), .width = c(.95), colour = "#006c66") +
  scale_fill_brewer(palette = "Greys") + 
  scale_x_continuous(limits = c(0,80), breaks = seq(0, 80, 5)) + 
  scale_y_continuous(limits = c(0,4)) + 
  guides(fill = "none") +
  labs(x = "Age in years", y = "Mean click distance in target widths", fill = "")

prediction_plot

# saveRDS(prediction_plot, file = "../saves/lifespan_modelplot.rds")
# ggsave("../figures/lifespan_modelplot.png", width = 10, height = 6, scale = 0.7, bg = "white")
```

>>>>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidybayes) # for stat_halfeye, add_predictive_draws
library(tidyboot) # for bootstrapped CIs
library(brms) # modeling
library(cmdstanr) # modeling
check_cmdstan_toolchain(fix = TRUE, quiet = TRUE)

@@

lifespan_plot

ggsave("../figures/lifespan_plot.png", width = 8, height = 4, scale = 1.2)
saveRDS(lifespan_plot, "../saves/lifespan_plot.rds")
```

@@

```{r draws_winning_model}
msplines <- readRDS("../saves/lifespan_msplines.rds")

mdraws <- mdata %>%
  add_predicted_draws(msplines) %>% 
  ungroup() %>% 
  select(-c(.row, .chain, .iteration)) %>%
  rename(draw = .draw, predicted_value = .prediction)

write.csv(mdraws, "../saves/lifespan_mdraws.csv", quote = F, row.names = F)
saveRDS(mdraws, "../saves/lifespan_mdraws.rds")
```

```{r prediction_plot_winning_model}
### this sections takes a while to run

# mdraws <- readRDS("../saves/lifespan_mdraws.rds")

mdraws %>%
  ggplot(aes(x = age)) +
  stat_lineribbon(aes(y = predicted_value), .width = c(.95), colour = "#006c66", fill = "lightgrey") +
  geom_jitter(aes(y = mean_dist), colour = "darkgrey", size = 1.5, alpha = 0.8) +
  scale_x_continuous(limits = c(0,80), breaks = seq(0, 80, 5)) +
  scale_y_continuous(limits = c(0,4)) +
  labs(x = "Age in years", y = "Mean click distance in target widths")

# prediction_plot

# saveRDS(prediction_plot, file = "../saves/lifespan_modelplot.rds")
ggsave("../figures/lifespan_modelplot.png", width = 8, height = 5, scale = 1, bg = "white")
```

```{r smooths}
lifespan_smooths <- mdata %>%
  ggplot(aes(x = age, y = mean_dist)) +  
  geom_jitter(colour = "grey", size = 1.5, alpha = 0.8) + 
  geom_smooth(method = lm, se = F, aes(colour = "A")) +
  geom_smooth(method = lm, formula = y ~ poly(x, 2), se = F, aes(colour = "B")) +
  geom_smooth(method = lm, formula = y ~ poly(x, 3), se = F, aes(colour = "C")) +
  geom_smooth(method = loess, se = F, aes(colour = "D")) +
  geom_smooth(method = lm, formula = y ~ splines::bs(x, 5), se = F, aes(colour = "E")) +
  scale_fill_brewer(palette = "Greys") + 
  scale_x_continuous(limits = c(0,80), breaks = seq(0, 80, 5)) + 
  scale_y_continuous(limits = c(0,4)) + 
  scale_color_manual(name = "Smooth method", 
                     breaks = c("A", "B", "C", "D", "E"),
                     values = c("#c6d325", "#00b1ea", "#29485d", "#9D3BBD", "#F71C8D"),
                     labels = c("linear", "quadratic", "cubic", "loess", "splines (k=5)")) +
  labs(x = "Age in years", y = "Mean click distance in target widths")

lifespan_smooths

saveRDS(lifespan_smooths, file = "../saves/lifespan_smooths.rds")
ggsave("../figures/lifespan_smooths.png", width = 10, height = 6, scale = 0.7, bg = "white")
```
